Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-09 paper.qmd
Tried add hist..need to change

@@

@@

@@

hex_grid_coloured_two_curvy2 +
  hex_grid_coloured_two_curvy1 +
  hex_grid_coloured_two_curvy3 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

>>>>

boxplot2 <- ggplot(df_bin_centroids_two_curvy, 
       aes(x=bin_counts)) + 
  geom_histogram()

@@

boxplot1 <- ggplot(df_bin_centroids2, 
                   aes(x=bin_counts)) + 
    geom_histogram()

@@

boxplot3 <- ggplot(df_bin_centroids3, 
                   aes(x=bin_counts)) + 
    geom_histogram()

@@

hex_grid_coloured_two_curvy2 +
  hex_grid_coloured_two_curvy1 +
  hex_grid_coloured_two_curvy3 +
  boxplot1 + boxplot2 + boxplot3 +
  plot_layout(guides='collect', ncol = 3) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```
